---
title: "Lab 3: Post Lab"
format: html
---

## Data Load

```{r}
#import data from this website

wine_quality <- readr::read_delim("https://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality-red.csv",delim=';')
 
```


## Design a research question

Examine the data to come up with an interesting research question based on the wine data. It is a large collection of wine attributes and quality ratings to indicate the sommlier's rating of the wine.

## Explore the data

Create some exploratory tables or charts to help you better understand possible relationships

## Use a Tidymodel framework to conduct your analysis.


```{r}
set.seed(123)

qlty_split <- initial_split(wine_quality, prop = 0.80,strata = quality)
  ### stratified on `wine quality`; training and test splits will both have ~60/40% survived = 0/1
qlty_train_df <- training(qlty_split)
qlty_test_df <- testing(qlty_split)
```

```{r}
qlty_train_df %>%
  group_by(quality) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(prop = n / sum(n))

qlty_test_df %>%
  group_by(quality) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(prop = n / sum(n))
```



## Visualize

Present your final results and upgrade this document's YAML to a professional level quality.
